\documentclass[a4paper,11pt]{article}

\setlength{\oddsidemargin}{0 in}
\setlength{\evensidemargin}{0 in}
\setlength{\topmargin}{-0.6 in}
\setlength{\textwidth}{6.5 in}
\setlength{\textheight}{8.5 in}
\setlength{\headsep}{0.75 in}
\setlength{\parindent}{0 in}
\setlength{\parskip}{0.1 in}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tikz-cd}
\usepackage{mathrsfs}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{enumitem}
\usepackage{yfonts}
\usepackage{ dsfont }
\usepackage{soul}
\usepackage{ulem,xpatch}
\usepackage{tabularx}
\usepackage{setspace}
\usepackage[
    type={CC},
    modifier={by-nc-nd},
    version={4.0},
]{doclicense}
\usetikzlibrary{matrix,shapes,arrows,positioning,chains}


\newcommand{\soutthick}[1]{%
    \renewcommand{\ULthickness}{2.4pt}%
       \sout{#1}%
    \renewcommand{\ULthickness}{.4pt}% Resetting to ulem default
}

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}

\newtheorem{defn}[thm]{Definition}
\newtheorem{eg}[thm]{Example}
\newtheorem{ex}[thm]{Exercise}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{claim}[thm]{Claim}
\newtheorem{rmk}[thm]{Remark}

\newcommand{\ie}{\emph{i.e.} }
\newcommand{\cf}{\emph{cf.} }
\newcommand{\into}{\hookrightarrow}
\newcommand{\dirac}{\slashed{\partial}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\LieT}{\mathfrak{t}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\A}{\mathds{A}}

\DeclareMathOperator{\lcm}{lcm}
\DeclareMathOperator{\ord}{ord}


\title{\textbf{STA305 Mini Project Notes}}

\author{Jiaqi Bi, University of Toronto}


\begin{document}

% Define block styles
\tikzset{
decision/.style={
    diamond,
    draw,
    text width=4em,
    text badly centered,
    inner sep=0pt
},
block/.style={
    rectangle,
    draw,
    text width=10em,
    text centered,
    rounded corners
},
cloud/.style={
    draw,
    ellipse,
    minimum height=2em
},
descr/.style={
    fill=white,
    inner sep=2.5pt
},
connector/.style={
    -latex,
    font=\scriptsize
},
rectangle connector/.style={
    connector,
    to path={(\tikztostart) -- ++(#1,0pt) \tikztonodes |- (\tikztotarget) },
    pos=0.5
},
rectangle connector/.default=-2cm,
straight connector/.style={
    connector,
    to path=--(\tikztotarget) \tikztonodes
}
}

\setstretch{1.1}
\begin{titlepage}
\end{titlepage}

\maketitle
\vspace*{\fill}
\doclicenseThis

\newpage

\section{First Discussion}
Background: Females nowadays really care about their lower leg hairs. 

Our topic will be ``If you shave hair, it comes back thicker." An experiment needs to be carried out with realistic situation and plan. The \underline{target population} for our experiment design will be the hair on the lower leg of female populations within the age group of 15-50 in the world because males and upper age groups tend not to shave their leg hairs mostly, the sample can be 100 females with different races (\underline{sample size}). The \underline{experimental unit} will be the female selected for sample purposes of our experiment. Different treatment for two groups (\underline{2 groups}): 
\begin{itemize}
\item Treatment Group: Females shave their left lower leg hairs using the razor; Shave at the beginning of each month, the test lasted for a quarter measure the thickness. 
\item Control Group: Females do not shave right leg hair.
\end{itemize}
Note that treatment groups and control groups are \underline{identical} in every possible way, except for the treatment. I.e., minimize the confounding variables. 

Thickness: Subjectively measured by the researcher. 

%\hl{Questions raised during the beforehand discussion:}
%\begin{enumerate}
%\item \hl{How do you define ``thicker"? Speed of growing, or others?}
%\item \hl{Does the "shave" mean totally shaved, or shave a little bit?}
%\item \hl{Does only nominal variable count as ``Factors"?}
%\item \hl{Should we consider the race in our experimental design?}
%\end{enumerate}

\underline{Variables} during the experiment: response variables will be a dummy variable that whether the shaved leg hair becomes thicker than the not shaved one, the independent variables will be whether the participant shaved the leg hair or not with two levels, level 1 is shaved less than 3 times, level 1 is shaved 3 times. The response variable is an Subjective Response because we are going to ask researchers to measure subjectively. The nuisance variablle includes: Gender, with levels of males and females; Races, with levels of Black, Caucasian, Asian, Hispanic, etc. The experiment lies under a \underline{Between-Subjects design} since we only decide about if the experimental unit shaves or not. 

We plan to take this experiment as a \underline{repeated measure design}. The nuisance variables might occur in the experiment has: 
\begin{itemize}
\item Sleeping hours
\item Vitamin consumption
\item Diet habits
\end{itemize}

\textbf{Principles of the experiment:} 
\begin{itemize}
\item Control: They all have great health conditions, no extra nutritions intake. Shave once at the beginning of the month, without body lotion. Using the same brand razor. 
\item Blocking: We will treat \underline{age groups} as our blocks, races.
\item Randomization: Since these females may have different eating habits, we will use the randomization. 
\item Replication: Treatment Level: We take many participants in the treatment group, 
Experiment Level: We can replicate the entire experiment in other regions. 
\end{itemize}

\subsection{Blinding, by Jiaqi Bi \& Lanruo Li}
%\textbf{Possible scheme 1: No blindings}

%Since the researchers and participants both will know if their hairs are shaved obviously, and after one month, researchers will measure the thickness. The measurement is an objective measures, therefore knowing the treatment does not effect the responses. 

\textbf{Single blinding}

Our participant is going to know whether he/she is about to take the treatment, i.e., shave their hairs. However, our researchers that are going to measure the thickness will not know whether the participant has shaved hairs before or not because the measurement is a subjective measures, such that if they know the treatment beforehand, it might affect their judgments. 

\subsection{Balance, by Lei Cao \& Le Shen}

Our experiment is balanced since there are two treatment groups in our experiment, one treatment
group will shave their left lower leg hair and the other control group will not. Shave their right lower leg.



%\subsection{Some new ideas added by Yuika Cho}

%Give them same food for each treatment group

%Shave a specific area of hair where hair growth is more consistent comparing to front hairline and vertex (where baldness usually starts to occur)

%We can choose hair above one side of ear

%Size of the area being shaved (ie. 3 cm by 3 cm)

%Length of hair strand: starting from root and measure 5 cm down for both before and after

%Before samples: we shave the original hair from the root and keep it with a length of 5 cm
%After samples: when the shaved area of hair grows back, we do the same thing as the before samples.

%\begin{tikzpicture}
%\matrix (m)[matrix of nodes, column  sep=2cm,row  sep=8mm, align=center, nodes={rectangle,draw, anchor=center} ]{
%    |[block]| {Start}              &  \\
%    |[block]| {Choose an area of hair (i.e., above left ear) }               &                                           \\
%    |[block]| {Shave from root}          &                                             \\
%   |[block]| {measure 5cm\footnotemark from here}    &       |[block]| {Let it grow back}                                       \\
%    |[block]| {Cut the extra length, keep 5cm leangth}         &      |[block]| {Shave from root}                     \\
%            &    |[block]| {Measure 5cm\footnotemark[1] from root}                              \\
 %                    &       |[block]| {Get rid of extra length and keep 5cm length of hair}                                 \\       
%};
%\path [>=latex,->] (m-1-1) edge (m-2-1);
%\path [>=latex,->] (m-2-1) edge (m-3-1);
%\path [>=latex,->] (m-3-1) edge (m-4-1);
%\path [>=latex,->] (m-4-1) edge (m-5-1);
%\path [>=latex,->] (m-3-1) edge (m-4-2);
%\path [>=latex,->] (m-4-2) edge (m-5-2);
%\path [>=latex,->] (m-5-2) edge (m-6-2);
%\path [>=latex,->] (m-6-2) edge (m-7-2);


%\end{tikzpicture}

%\footnotetext{The length is subject to change if males have shorter hair in average}

\subsection{Control \& Treatment Group, Mengyu Lei, Yirun Mao}
We consider the group of ``shaving the left lower leg hair" to be the treatment group as it is the fundamental of this experiment, and we consider the group of ``not shaving the right leg hair" to become the control group to contrast the data between these groups. Because we would like to measure their difference of the thickness. In this experiment, we do not need the placebo since our measurement will be subjective. 

\subsection{Limitation}
\begin{enumerate}
\item We cannot control the male sex hormone in each female, females have different thickness from their births. 
\item Different genetic heredity for each female. 
\item Not sure if they have shaved before or not. 
\end{enumerate}

\newpage


\section{Final Draft}

Background: Test the effect of the treatment on the thickness of the hair between shaved group and non-shaved group. 

Objective: Test whether the hair becomes thicker after shaving. 

Limitation: Before the experiment, we cannot control their nutritions intake that it may lead to some biased results. 


\newpage




\section{Reminders}
Office hours: Thursday 9:30-10:30AM EDT (Toronto Time)

\subsection{Work Assign}

\sout{\textbf{Deadline: 8:30PM Wed.  (Toronto Time); 8:30AM Thur. (Beijing)}}

\sout{\textbf{Meeting before office hour: 8:00AM Thurs.  (Toronto Time); 8:00PM Thurs. (Beijing)}}

\textbf{PPT First Draft (At least all pages needed to be filled), Deadline: Sat. Jul.17 11:00PM}

\textbf{PPT Final Draft, Deadline: Sun. Jul. 18 8:00PM}

\textbf{Video Recordings, Jul. 18 8:00PM-11:00PM}

\textbf{Deadline of Entire Mini Project Group Work: Before Monday!}









\end{document}




